Empty Homes V1

### 2017-05-25 EmptyHomesV1.Rmd
Remove DAT
Changed the way maps are plotted so the DAT dataframe is no longer needed. It also allows for all data on a region to be plotted even when that data is missing

Lam2 <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
    StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))

Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%
  setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,c(2:5, 24:25)]), Empty = LowUse - Empty.Class.A-Empty.Class.B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

LAMDAT <- AG %>% filter(LAD11NM == "Lambeth") %>% 
  left_join(., select(Lambeth, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Islington

Islington <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4] %>% setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,-c(1,12,13)]), Empty = LowUse ) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

ISL2 <- Islington %>% mutate(LowUsePerc = LowUse/Homes)

ISLDAT <- AG %>% filter(LAD11NM == "Islington") %>% 
  left_join(., select(Islington, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Greenwhich
list.files()
wardnames %>% filter(grepl("city", LAD11NM))

Greenwich <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% ungroup %>%
  mutate(Exemption.type = trimws(Exemption.type))  %>%
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,c(2,3,4,21,22)]), Empty = LowUse -  EMPTY.CLASS.B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

Greenwhich2 <- Greenwich %>% mutate(LowUsePerc = signif(LowUse/Homes*100,3))

GREDAT <- AG %>% filter(grepl("Greenwich", LAD11NM)) %>% left_join(., select(Greenwich, Admin_ward_code, LowUse, Empty))

@@

test <- read.xlsx("Camden Exemptions LSOA - 20891480.xlsx")[1:4]

Camden <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
  group_by(Discount.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Discount.type, Counts, fill = 0) %>% 
  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse - B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

CAMDAT <- AG %>% filter(LAD11NM == "Camden") %>% 
  left_join(., select(Camden, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Bromley <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,1:4] %>%
  setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,c(6:8,29:31)]), Empty=LowUse - Empty.Class.B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

BRODAT <- AG %>% filter(LAD11NM == "Bromley") %>% 
  left_join(., select(Bromley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Haringey <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] %>%
    setNames(make.names(names(.))) %>%
  group_by(Exemption...Discount.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>%
  spread(., key = Exemption...Discount.type, 
         value = Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,21:25]), Empty=LowUse - PCLB0) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

HARDAT <- AG %>% filter(LAD11NM == "Haringey") %>% 
  left_join(., select(Haringey, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Sutton <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,1:6] %>%
    setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>%
  spread(., key = Exemption.type, 
         value = Counts, fill = 0) %>%
    setNames(make.names(names(.)))%>%
  mutate(LowUse = rowSums(.[,-1]), Empty=LowUse - PCLB0) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

SUTDAT <- AG %>% filter(LAD11NM == "Sutton") %>% 
  left_join(., select(Sutton, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Richmond

Richmond <- read_csv("Richmond_2.csv" )[1:4] %>% setNames(make.names(names(.))) %>%
  rename(Exemption.type = Discount.type) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .)) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>%
    mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

RICDAT <- AG %>% filter(LAD11NM == "Richmond upon Thames") %>% 
  left_join(., select(Richmond, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Hillingdon <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4] %>% mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .)) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>%  
  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse- Class.B.Second.Home) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

HILDAT <- AG %>% filter(LAD11NM == "Hillingdon") %>% 
  left_join(., select(Hillingdon, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2,19,20)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BEXDAT <- AG %>% filter(LAD11NM == "Bexley") %>% 
  left_join(., select(Bexley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Chelsea <- read.xlsx( "Kensington and ChelseaDiscountsLSOA.xlsx" , colNames = TRUE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")

#Barking
Bark <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2,3,6,7)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BARKDAT <- AG %>% filter(LAD11NM == "Barking and Dagenham") %>% 
  left_join(., select(Bark, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
  setNames(c("ExemAG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")ption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2:8)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Newham <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

# Chelsea
# Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))
# 
# Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(Ward) %>%
#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related, Empty..50..premium, Moorings , na.rm = TRUE),
#          LowUse = Empty + Second.Homes) %>% ungroup
# 
# Chelsea[is.na(Chelsea)] <-0
# rm(Chelwards)
# 
# Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
#   mutate(LowUsePerc = LowUse/WardHomes)
# 
# cor(Chel2$PrimePerc, Chel2$LowUsePerc)
# cor(Chel2$MeanPrice, Chel2$LowUsePerc)
# 
# Chel2 %>%
#   mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>%
#   ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() +
#   geom_smooth(method ="lm", se = FALSE) +
#   labs(title = "Relationship between % of Prime Sales and % Low Use",
#        x = "% of properties sold in 2016 over £1M by electoral ward",
#        y = "% of properties either empty or second homes") +
#   theme(plot.title = element_text(hjust = 0.5))  +
#   coord_cartesian(xlim = c(15,78), expand = TRUE)
# 
# 
# 
# CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
#   filter(WD16NM!= "Kensal Green")

@@

SingleB <- AG %>% filter(grepl("Kensington", LAD11NM))%>% 
  left_join(., select(Chelsea, Admin_ward_code, WardLowUse, WardLowUsePerc)) %>% 
  filter(WD16NM!= "Kensal Green") %>%
  mutate(WardLowUsePerc = WardLowUsePerc*100)

ggplot(SingleB) + 
  geom_polygon( aes(long, lat, group = group, fill = WardLowUsePerc), 
colour = alpha("black", 1/4), size = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(SingleB$WardLowUsePerc, na.rm = TRUE)) +
  labs(title = "Kensington and Chealsea: Ward Level % Low Use", fill = "Percentage") +
  theme(plot.title = element_text(hjust = 0.5)) +
    theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

@@

ggplotly() #STFD!
#Single borough detail

Singlevis <- AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
  left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
  ungroup %>%
  filter(WD16NM!= "Kensal Green") %>%
  mutate(LowUsePerc = round(LowUse/Homes.y*100), 
         EmptyPerc = round(Empty/Homes.y*100),
         EmptyPercRank = percent_rank(Empty/Homes.y))

ggplot(Singlevis, aes(long, lat, group = group, fill = LowUsePerc))+ 
  geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(Singlevis$LowUsePerc))+
  theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())+ 
  ggtitle("Kensington and Chelsea Low use")

Bourough2 <- Chelsea %>% ungroup %>% mutate(LowUsePerc = LowUse/Homes, 
         EmptyPerc = Empty/Homes,
         EmptyPercRank = percent_rank(Empty/Homes))

@@

PlotMap(test,"Hull", variable = "WardLowUsePerc")

>>>>

Lambethinfo <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
    StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))

#Islington is exemptions only

Islingtoninfo <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4]%>%  
    StructureData(., lowuse = c(2:11,14:18))

#Greenwhich

Greenwichinfo <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>%  
    StructureData(., c(2,3,4,21,22), c(3,4,21,22))

@@

Camdeninfo <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
 StructureData()

@@

Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
  StructureData(c(6:8,29:31))

@@

#Haringey is funney and has to be worked over a bit first
Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)]

Haringeyinfo <- data_frame(Discount = rep(Haringey$`Exemption./.Discount.type`, Haringey$Count.of.Exemptions.by.Post.Code),
           LSOA = rep(Haringey$LSOA_CODE, Haringey$Count.of.Exemptions.by.Post.Code)) %>%
  mutate( a= NA, b = NA) %>%
  StructureData(21:25)

@@

Suttoninfo <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,c(1,4:6)] %>%
  StructureData()

#Richmond
Richmondinfo <- read_csv("Richmond_2.csv" )[1:4]%>%
  StructureData()

@@

Hillingdoninfo <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4]%>% 
  StructureData()

@@

Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
StructureData

@@

Chelseainfo <- read_excel( "Kensington and ChelseaDiscountsLSOA.xlsx" )[,1:4] %>%
  StructureData()

#Barking
Barkinginfo <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE)[,1:4] %>%
  StructureData(c(2,3,6,7))

@@

Barnetinfo <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
  StructureData(2:8)

@@

Newhaminfo <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE)[,1:4] %>%
  StructureData(2)

test <- ls(pattern = "info") %>% map_df(~eval(parse(text=.x)))

@@

@@

PlotMap(Chelsea, "Chelsea")

@@

ggplotly() #STFD!

@@

PlotMap(test, AG, variable = "WardLowUsePerc")
